Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2013-10-08 exp1/iswc2013.tex
Correct post-publication typo
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@653 43ef1190-90fd-4dd7-a769-d0121f02b80e

We perform the test as a one-sided hypothesis test where $H_0$ is that
the mean of the vectors are equal and $H_1$ is that mean sof the
vectors representing the new implementation is lower. In this example,
we find that the available data supports the assertion that the new
implementation is better with a high probability, $p=1.16 \cdot
10^{-07}$.

>>>>

We perform the test as a one-sided hypothesis test where $H_0$ is that
the mean of the vectors are equal and $H_1$ is that means of the
vectors representing the new implementation is lower. In this example,
we find that the available data supports the assertion that the new
implementation is better with a high probability, $p=1.16 \cdot
10^{-07}$.
